%-------------------------
% Resume in Latex
% Author : Vishal Dongre
% License : MIT
%------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    % Full Name
    \textbf{\Huge Vishal Dongre} \\ \vspace{5pt}
    
    % Contact Info
    \small 
    % Phone
    \faPhone* \texttt{7400813134} \hspace{1pt} $|$
    % Email
    \hspace{1pt} \faEnvelope \hspace{2pt} \href{mailto:xvishaldongre@gmail.com}{\underline{xvishaldongre@gmail.com}} \hspace{1pt} $|$
    % Website
    \hspace{1pt} \faLink \hspace{2pt} \href{https://xvishaldongre.com}{\underline{xvishaldongre.com}} \hspace{1pt} $|$
    % LinkedIn
    \hspace{1pt} \faLinkedin \hspace{2pt} \href{https://linkedin.com/in/xvishaldongre}{\underline{linkedin.com/in/xvishaldongre}} \hspace{1pt} $|$
    % \hspace{1pt} \faMapMarker* \hspace{2pt}\texttt{India}
    \\ \vspace{-3pt}
\end{center}

%-----------PROFILE-----------
\section{PROFILE}
    \resumeSubHeadingListStart
      \resumeSubItem{As a software engineer with a robust background in cloud architecture and automation, I possess skills in various programming languages, including Python, JavaScript, and GoLang. I also have a deep understanding of cloud computing, CI/CD tools, along with containerization and container orchestration.

      Overall, I am a dedicated and results-driven software engineer, eager to tackle new challenges and contribute to the success of any organization.}
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, JavaScript, Go} \\
     \textbf{Cloud Platforms}{: AWS, Google Cloud Platform} \\
     \textbf{Developer Tools}{: Git, Docker, Kubernetes, Nomad, Terraform, Vagrant, Ansible, GitHub Actions, Datadog, VS Code} \\
     \textbf{Libraries}{: Boto3, Pandas, Playwright, Selenium, BeautifulSoup, FastAPI, Requests, Pytest, Numpy} \\
     \textbf{Other}{: Linux, Bash, SQL, NoSQL, REST API, CI/CD, HCL, YAML, Agile, Scrum, Kanban, Trello, Jira, Confluence} \\
    }}
 \end{itemize}
 
%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {HCL Tech}{Dec 2021 - Present}
      {Analyst}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{\textbf{Led a team of 3 developers} in designing and maintaining monitoring systems for AWS infrastructure and custom applications using Datadog. Implemented IaC with Terraform, reducing deployment time by 30\% and troubleshooting time by 50\%.}
        \resumeItem{Developed \textbf{"Synthetic Monitoring Browser and API upchecks"} for monitoring website and API uptime using Python Playwright and deployed to AWS Fargate. \textbf{Migrated 30+ custom applications} from Datadog synthetics, leading to 30\% cost savings and 70\% time savings through automated deployments using Terraform.}
        \resumeItem{Worked with business customers to automate manual processes such as pulling orders, comparing orders, storing data in S3 and Google Sheets, and sending logs to Datadog and Slack. This resulted in \textbf{\$300,000+ cost savings} and reduced manual effort.}
        \resumeItem{Collaborated with AWS Professional Services to deploy AWS Workspaces VDI, \textbf{serving 500+ contractors} across multiple regions.}
        \resumeItem{Created custom images and bundles for AWS Workspaces depending on customer and security requirements.}
        \resumeItem{Automated UiPath nuget package deployment using GitHub Actions, cutting deployment time by 50\%.}
        \resumeItem{Automated UiPath Server installation and configuration with Terraform and Ansible, reducing deployment time by 50\%.}
        \resumeItem{Designed and maintained Datadog dashboards and monitors with Terraform, achieving a 70\% reduction in deployment time.}
      \resumeItemListEnd

    \resumeSubheading
      {Startek India (Aegis)}{July 2018 - June 2019}
      {Customer Service Executive}{Chhindwara, India}
      \resumeItemListStart
        \resumeItem{Provided L2 support to Paytm customers via chat on Salesforce CRM.}
        \resumeItem{Automated daily reports using Excel Macros, reducing report generation time by 50\%.}
        \resumeItem{Contributed to Standard Operating Procedure (SOP) documentation for the team.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section {EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Computer Application (BCA)}{2018 - 2021}
      {Government Autonomous P.G. College}{Chhindwara, India}
          \resumeItemListStart
        \resumeItem {\textbf{Coursework}: Cloud Computing, Database Management Systems, Web Development, Programming in C, C++ and Java, Data Structures and Algorithms, Software Engineering, Network Security, Operating Systems}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

% %-----------PROJECTS-----------
\section {PROJECTS}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AWS Infrastructure Monitoring} $|$ \emph{Python, Datadog, Terraform, AWS}}{Dec 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Developed \textbf{Infrastructure Monitoring} for AWS infrastructure using Datadog and Terraform.}
            \resumeItem{Implemented \textbf{IaC} with Terraform, reducing deployment time by 30\% and troubleshooting time by 50\%.}
            \resumeItem{Designed and maintained Datadog dashboards and monitors with Terraform, achieving a 70\% reduction in deployment time.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Synthetic Monitoring} $|$ \emph{Python, Playwright, AWS Fargate}}{Dec 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Developed \textbf{"Synthetic Monitoring Browser and API upchecks"} for monitoring website and API uptime using Python Playwright and deployed to AWS Fargate.}
            \resumeItem{Migrated 30+ custom applications from Datadog synthetics, leading to 30\% cost savings and 70\% time savings through automated deployments using Terraform.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{UiPath Automation} $|$ \emph{UiPath, GitHub Actions, Terraform, Ansible}}{Dec 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Automated UiPath nuget package deployment using GitHub Actions, cutting deployment time by 50\%.}
            \resumeItem{Automated UiPath Server installation and configuration with Terraform and Ansible, reducing deployment time by 50\%.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{AWS Workspaces VDI} $|$ \emph{AWS Workspaces, AWS Directory Service}}{Dec 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Collaborated with AWS Professional Services to deploy AWS Workspaces VDI, serving 500+ contractors across multiple regions.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{CERTIFICATIONS}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Cloud Digital Leader}{Issued Sep, 2023 - Expires Sep, 2026}
      {Google Cloud}{Credential ID: 81863984}
      \resumeItemListStart
        \resumeItem{Link: \href{https://www.credential.net/ac8b2017-57db-4e03-a908-fbdf5af86321}{\underline{Google Cloud Digital Leader Certification}}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
\end{document}